---
title: "sentimental analysis"
author: "Prem Kumar Kamasani"
date: "March 28, 2019"
output:
  word_document: default
  html_document: default
---

```{r}
pos.words <- read.csv("positive.csv")
neg.words <- read.csv("negative.csv")
pos.words <- scan("positive.csv",what = 'character')
neg.words <- scan("negative.csv",what = 'character')
apple<-read.csv("apple1101.csv", header = TRUE, sep = ",");

```
pos.words variable has positive words. neg.words variable has negative words.
Data of apple tweets are taken from twitter api. 

Our aim is to find sentimental score as well emotion analysis on tweets of Apple.
positive word has score of +1 and negative word has score of -1.
Range of scores =[-5, +5]
```{r}
score.sentiment = function(sentences, pos.words, neg.words, .progress='.progress')
{
  require(plyr)
  require(stringr)
  scores = laply(sentences, 
                 function(sentence, pos.words, neg.words)
                   {
                    sentence = gsub('[[:punct:]]', '', sentence)
                    sentence = gsub('[[:cntrl:]]', '', sentence)
                    sentence = gsub('\\d+', '', sentence)
                    sentence = tolower(sentence)
                    word.list = str_split(sentence, '\\s+')
                    words = unlist(word.list)
                    pos.matches = match(words, pos.words)
                    neg.matches = match(words, neg.words)
                    pos.matches = !is.na(pos.matches)
                    neg.matches = !is.na(neg.matches)
                    score=sum(pos.matches)-sum(neg.matches)
                    return(score)
                  },
                 pos.words, 
                 neg.words,
                 .progress='.progress' )
  scores.df = data.frame(score=scores, text=sentences)
  return(scores.df)
}

```

```{r}
apple<-as.data.frame(apple)
result <- score.sentiment(apple$text,pos.words,neg.words)
summary(result$score)

```

```{r}
hist(result$score,col ="red", main ="Score of tweets",ylab = " Count of tweets", xlab = "score")


```
From the above bar graph we can observe that neutral tweets are more.
```{r}
library(syuzhet)
library(lubridate)
library(ggplot2)
library(scales)
library(reshape2)
library(dplyr)
```
we use these libraries to calculate the scores of emotions for Apple tweets data. 
```{r}
apple<-read.csv("apple1101.csv", header = TRUE, sep = ",")
tweets<-iconv(apple$text)
sentiments<-get_nrc_sentiment(tweets)
barplot(colSums(sentiments), las=2, col=rainbow(10),ylab = "count", main = "Sentiments for Apple Tweets")


```
